
\documentclass[
10pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}



\makeatletter
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\makeatother

\input{structure.tex} % Include the structure.tex file which specified the document structure and layout
% -----------------------------------------------------------------------
\usepackage[english]{babel}
\usepackage[text={5.5in,8.3in},centering]{geometry}
\usepackage{hyperref}
% ------------------------------

\pagestyle{plain}
% -----------------------------------------------------------------------
% -----------------------------------------------------------------------

\title{List of  publications}
\author{Frank van der Meulen}
\begin{document}
%\begin{center}
%{\Large  {\bf Curriculum vitae Frank van der Meulen }}
%
%%\medskip
%%
%%{\large Delft Institute of Applied Mathematics}
%\end{center}

\maketitle
\tableofcontents


\bigskip

\noindent All papers are peer reviewed, except  papers marked by a $\square$.

\section{Statistical inference for stochastic processes}

\begin{enumerate}

\item {\sc F.H. van der Meulen and S. Sommer} (2025) {\it Backward Filtering Forward Guiding}. To appear in Journal of Machine Learning Research.

\item {\sc M.A. Corstanje, F.H. van der Meulen, M. Schauer and S. Sommer} (2025) {\it Simulating conditioned diffusions on manifolds}. Accepted for publication in Bernoulli.

\item {\sc G. Yang, F.H. van der Meulen and S. Sommer} (2025) {\it Neural guided diffusion bridges}. ICML 2025.

\item {\sc M.A. Corstanje and F.H. van der Meulen} (2025) {\it Guided simulation of conditioned chemical reaction networks}. Statistical Inference for Stochastic Processes {\bf 28}(8). 

\item {\sc T. Pieper-Sethmacher, F.H. van der Meulen and A.W. van der Vaart} (2025) {\it On a class of exponential changes of measure for stochastic PDEs},  Stochastic Processes and their Applications {\bf 185}, 1--19. 

\item {\sc D. Belomestny, F.H. van der Meulen, and P. Spreij} (2023), {\it Nonparametric Bayesian inference for stochastic processes with piecewise constant priors}, Mathematics of Risk 2022 MATRIX Annals, Editors: David R. Wood, Jan de Gier, Cheryl E. Praeger, Terence Tao. MATRIX Book Series, Springer.

\item {\sc J. Bierkens, S. Grazzi, F.H. van der Meulen and M. Schauer} (2023) {\it  Sticky PDMP samplers for sparse and local inference problems},  Statistics and Computing {\bf 33}(1), article nr 8. 

\item {\sc M.A. Corstanje, F.H. van der Meulen and M. Schauer} (2023) {\it  Conditioning continuous-time Markov processes by guiding}, Stochastics, {\bf 95}(6), 963--996.

\item {\sc S. Gugushvili, F.H. van der Meulen, M. Schauer and P. Spreij} (2022), {\it  Nonparametric Bayesian volatility learning under microstructure noise}, Japanese Journal of Statistics and Data Science {\bf 6}(1), 551-571.

\item {\sc A. Arnaudon, F.H. van der Meulen, M.R. Schauer and S. Sommer} (2022), {\it Diffusion bridges for stochastic Hamiltonian systems and Shape Evolutions},  SIAM Journal on Imaging Sciences (SIMS), {\bf 15}(1), 293-323.

\item {\sc S. Sommer, M. Schauer and F.H van der Meulen}  {\it Stochastic flows and shape bridges} (2021). In Statistics of Stochastic Differential Equations on Manifolds and Stratified Spaces (hybrid meeting), number 48 in Oberwolfach Reports, Mathematisches For\-schungs\-institut Oberwolfach, 2021. doi: 10.4171/OWR/2021/48. \hspace*{\fill} $\quad \square$


\item {\sc M. Mider, M.R. Schauer and F.H. van der Meulen (2021)} {\it  Continuous-discrete smoothing of diffusions}, Electronic Journal of Statistics 15, 4295-4342.   


\item {\sc J. Bierkens, S. Grazzi, F.H. van der Meulen and M. Schauer (2021)} {\it A piecewise deterministic Monte Carlo method for diffusion bridges}, Statistics and Computing {\bf 31}(3).

\item {\sc J. Bierkens, F.H. van der Meulen and M.R. Schauer (2020)} {\it  Simulation of elliptic and hypo-elliptic conditional diffusions}, Advances in Applied Probability {\bf 52}, 173–-212.

\item {\sc F.H. van der Meulen, M. Schauer, S. Grazzi, S. Danisch and M. Mider (2020)} {\it  Bayesian inference for SDE models: a case study for an excitable stochastic-dynamical model},  \\ Nextjournal \url{https://nextjournal.com/Lobatto/FitzHugh-Nagumo}.\hspace*{\fill} $\quad \square$

\item {\sc F.H. van der Meulen and M.R. Schauer (2017)} {\it  Bayesian estimation of incompletely observed diffusions}, Stochastics {\bf 90}(5), 641--662.

\item {\sc F.H. van der Meulen and M.R. Schauer (2017)} {\it  Bayesian estimation of discretely observed multi-dimensional diffusion processes using guided proposals},  Electronic Journal of Statistics {\bf 11}(1), 2358--2396.

\item {\sc M.R. Schauer, F.H.  van der Meulen and J.H. van Zanten (2017)} {\it  Guided proposals for simulating multi-dimensional diffusion bridges}, Bernoulli {\bf 23}(4A), 2917--2950.

\item {\sc F.H. van der Meulen, M.R. Schauer and J.H. van Zanten (2014)} {\it  Reversible jump MCMC for nonparametric drift estimation for diffusion processes}, Computational Statistics and Data Analysis {\bf 71}, 615--632.

\item {\sc F.H. van der Meulen, M.R. Schauer, J. van Waaij (2017)} {\it   Adaptive nonparametric drift estimation for diffusion processes using Faber-Schauder expansions},  Statistical Inference for Stochastic Processes {\bf 21}(3), 603--628.

\item {\sc S. Gugushvili, F.H. van der Meulen, M.R. Schauer and P. Spreij (2020)} {\it  Non-parametric Bayesian estimation of a Holder continuous diffusion coefficient}, Brazilian Journal of Probability and Statistics {\bf 34}(3), 537--579. 

\item {\sc S. Gugushvili, F.H. van der Meulen, M.R. Schauer and P. Spreij (2020)} {\it  Fast and scalable non-parametric Bayesian inference for Poisson point processes}, \url{researchers.one}, corresponding code is on zenodo \url{https://zenodo.org/record/1215901#.Wtg3N9NuZTY}.

\item {\sc S. Gugushvili, F.H. van der Meulen, M.R. Schauer and P. Spreij (2018)} {\it  Nonparametric Bayesian volatility estimation}, MATRIX Annals, Editors: David R. Wood, Jan de Gier, Cheryl E. Praeger, Terence Tao. MATRIX Book Series, Vol {\bf 2}, Springer.

\item {\sc S. Gugushvili, F.H. van der Meulen and P.J. Spreij (2018)} {\it  A non-parametric Bayesian approach to decompounding from high frequency data}. Statistical Inference for Stochastic Processes {\bf 21}, 53--79.

\item {\sc S. Gugushvili, S., P. Spreij and F.H. van der Meulen (2015)} {\it  Non-parametric Bayesian inference for multi-dimensional compound Poisson processes}, Modern Stochastics: Theory and Applications {\bf 2}(1), 1--15.

\item {\sc F.H. van der Meulen and J.H. van Zanten (2013)} {\it  Consistent nonparametric Bayesian inference for discretely observed scalar diffusions}, Bernoulli {\bf 19}(1), 44–-63.

\item {\sc F.H. van der Meulen, A.W. van der Vaart and J.H. van Zanten (2006)} {\it  Convergence rates of posterior distributions for Brownian semimartingale models}, Bernoulli {\bf 12}(5), 863--888.

\item {\sc G. Jongbloed and F.H. van der Meulen (2006)} {\it  Parametric estimation for subordinators and induced OU-processes}, Scandinavian Journal of Statistics {\bf 33}(4), 825--847

\item {\sc G. Jongbloed, F.H. van der Meulen and A.W. van der Vaart (2005)} {\it   Nonparametric inference for L\'vy driven Ornstein-Uhlenbeck processes}, Bernoulli {\bf 11}(5), 759--791.

\item {\sc F.H. van der Meulen (2005)} {\it  Statistical estimation for Levy driven OU-processes and Brownian semimartingales}, Phd-thesis, Vrije Universiteit Amsterdam.\hspace*{\fill}  $\quad \square$
\end{enumerate}

%%%%%%%%%%%
\section{Deconvolution, decompounding, denoising, censoring...}

\begin{enumerate}

\item {\sc G. Jongbloed, F.H. van der Meulen and L. Pang (2022)} {\it  Bayesian nonparametric estimation in the current status continuous mark model}, Scandinavian Journal of Statistics {\bf 49}(3), 1329--1352.




\item {\sc G. Jongbloed, F.H. van der Meulen and L. Pang (2021)} {\it  Nonparametric Bayesian estimation of a concave distribution function with mixed interval censored data},  Brazilian Journal of Probability and Statistics {\bf 35}(3), 544-568.
\item {\sc G. Jongbloed, F.H. van der Meulen and L. Pang (2021)} {\it  Bayesian estimation of a decreasing density}, Brazilian Journal of Probability and Statistics {\bf  35}(2), 392--420.

\item {\sc S. Gugushvili, E. Mariucci and F.H. van der Meulen (2020)} {\it  Decompounding discrete distributions: a non-parametric Bayesian approach}, Scandinavian Journal of Statistics {\bf 47}(2), 464--492.

\item {\sc S. Gugushvili, F.H. van der Meulen, M.R. Schauer and P. Spreij (2019)} {\it  Bayesian wavelet de-noising with the Caravan prior}, ESAIM Probability and Statistics {\bf 23}, 947--978.

\item {\sc G. Jongbloed, G. and F.H. van der Meulen (2009)} {\it  Estimating a concave distribution function from data corrupted with additive noise},  Annals of Statistics {\bf 37}(2), 782--815. 

\end{enumerate}

\section{Applied  statistics}

\begin{enumerate}
\item {\sc M. Reijne, F.H. van der Meulen, F.C.T. van der Helm and A.L. Schwab} (2025) {\it A model based on cyclist fall experiments which predicts the maximum allowable handlebar disturbance from which a cyclist can recover balance},
Accident Analysis and Prevention {\bf 221}, article nr 108159,
1--12.


\item  {\sc R. Hindriks, F.H. van der Meulen, M. van Putten and P. Tewarie} (2025) {\it Unraveling high-order interactions in electrophysiological brain signals using elliptical distributions: Moving beyond the Gaussian approximation}. Journal of Physics: Complexity {\bf 6}(2), 1--15.

\item {\sc L. Gomaz, B. van Trigt, F. van der Meulen and D.J. Veeger} (2025) {\it Predicting elbow load based on individual pelvis and trunk (inter)segmental rotations in fastball pitching}, Sports Biomechanics {\bf 24}(11), 3296--3311. 
%\url{https://doi.org/10.1080/14763141.2024.2315230}.

\item {\sc L. Gomaz, D.J. Veeger, E. van der Graaff, B. van Trigt and F.H. van der Meulen (2021)} {\it  Individualised Ball Speed Prediction in Baseball Pitching based on IMU Data}, Sensors {\bf 21}(22), article nr 7442.  

\item {\sc R.B. Hageman, F.H. van der Meulen, A. Rouhan and M.L. Kaminski (2022)} {\it  Improved Risk-Based Inspection planning through in-service Hull Structure Monitoring of FPSO hulls}, Marine Structures {\bf 81}, 1--19.

\item {\sc L. M\'esz\'aros, F.H. van der Meulen, G. Jongbloed and G. el Sarafy (2021)} {\it Climate change induced uncertainties in Phytoplankton spring bloom dynamics}, Frontiers in Marine Science {\bf 8}, article nr 669951.


\item {\sc L. M\'esz\'aros, F.H. van der Meulen, G. Jongbloed and G. el Sarafy (2021)} {\it  A stochastic climate generator to complement existing climate change scenarios}, Stochastic Environmental Research and Risk Assessment (SERRA) {\bf 35}, 719--736.

\item {\sc K. Hartman, A. Wittich, J.J. Cai, F.H. van der Meulen and J.M.N. Azevedo (2016)} {\it  Estimating the age of Rissos dolphins (Grampus griseus) based on skin appearance},  Journal of Mammology {\bf 97}(2), 490--502.

\item {\sc F.H. van der Meulen, S. Luca, G. Overal, A. di Bucchianico and G. Jongbloed (2014)} {\it  Modeling a water purification process for quality monitoring}, Proceedings of the 98th Study Group Mathematics with Industry, 36--54.\hspace*{\fill}  $\quad \square$

\item {\sc F.H. van der Meulen, R. Hageman (2013)} {\it  Fatigue Predictions using Statistical Inference within the Monitas II Project}, Proceedings of the Twenty-hrid International Offshore and Polar Engineering, 463--471.\hspace*{\fill}  $\quad \square$

\item {\sc L.S.G.L. Wauben, W.M.U. van Grevenstein, R.H.M. Goossens, F.H. van der Meulen and J.F. Lange (2011)} {\it  Operative notes do not reflect reality in laparoscopic cholecystectomy}, The British journal of surgery. {\bf 98}(10), 1431--1436.

\item {\sc F.H. van der Meulen, M.B. Vermaat and P. Willems (2010)} {\it  Case Study: An application of Logistic Regression in a Six Sigma project in Healthcare}, Quality Engineering {\bf 23}, 113--124.

\item {\sc F.H. van der Meulen, H. de Koning and J. de Mast (2009)} {\it   Non-repeatable gauge R\&R studies assuming temporal or patterned object variation}, Journal of Quality Technology {\bf 41}(4), 1--14.

\item {\sc M.B. Vermaat, F.H. van der Meulen and R.J.M.M. Does (2008)} {\it  Asymptotic Behaviour of the Variance of the EWMA Statistic for Autoregressive Processes}, Statistics and Probability Letters {\bf 78(}12), 1673--1682.

\item {\sc H.J.J. Ramaker, E.N.M. van Sprang, J.A. Westerhuis, S.P. Gorden, F.H. van der Meulen and A.K. Smilde (2006)} {\it  Performance assessment and improvement of control charts for statistical batch process monitoring},  Statistica Neerlandica {\bf 60}(3), 339--360.

\end{enumerate}


\section{Outreach}


\begin{enumerate}
\item {\sc F.H. van der Meulen} (2025) {\it Statistiek: het onzichtbare zichtbaar maken}. Nieuw Archief voor Wiskunde {\bf 26}(2), 109--117. \hspace*{\fill}  $\quad \square$


\item {\sc A. di Bucchianico, L. Iapichino, N. Litvak, F.H. van der Meulen and R. Wehrens (2018)} {\it  Mathematics for Big Data}, Nieuw Archief voor wiskunde, 282--287. Reprinted in ``The Best Writing on Mathematics 2019''.\hspace*{\fill}  $\quad \square$



\item {\sc N. Litvak and F.H. van der Meulen (2015)} {\it  Networks \& Big Data}, Nieuw Archief voor Wiskunde {\bf 5}(2), 138--139.\hspace*{\fill}  $\quad \square$

\item {\sc G. Jongbloed and F.H. van der Meulen (2011)} {\it  Geurproef niet meer in gebruik in strafzaken (in dutch)}, Stator, pages 38-43.\hspace*{\fill}  $\quad \square$

\item {\sc F.H. van der Meulen (2021)} {\it  Een uitnodiging tot data science met R}  (on my website, in dutch).\hspace*{\fill}  $\quad \square$

\item {\sc F.H. van der Meulen and M.R. Schauer (2017)} {\it  On residual and guided proposals for diffusion bridge simulation}.  \hspace*{\fill} $\quad \square$



\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%







\end{document}


